### 2022-11-15 files/Overview.tex
Overview v1

\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Overview}
\begin{itemize}
	\item Chapter 1: Models, Dimensionless, Variational Forms, Modal Analysis
	\item Chapter 2: Example Weak Variational, Existence and Uniqueness from [VV02], Application to example
	\item Chapter 3: Example Galerkin, Convergence of Galerkin [BV13], Application to example, Convergence of Eigenvalues using FEM
	\item Chapter 4: Eigenvalues of Timo [VV06], Example of applications on models, Emperical Study of validity [SP06], Cantilever with Tip-Body (Example why need validity)
	\item Chapter 5: FEM of 2D, 3D, and Plate
	\item Chapter 6: Validity of 1D, Validity of 2D, Validity of Plate
	\item Chapter 7: Conclusion
\end{itemize}

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}

\section{Comparison of models}
\subsection{Introduction}
\subsection{Model problem for a three-dimensional elastic solid}
\subsubsection{Equations of motion and constitutive equations}
\textbf{Equation of motion}
\subsubsection{Dimensionless form}
\subsubsection{Model problems}
\textbf{Problem 3D-1}\\
\textbf{Problem 3D-2}
\subsubsection{Variational form}
\textbf{Bilinear forms and integral}\\
\textbf{Test functions}\\
\textbf{Problem 3D-1V}
\subsubsection{Plane stress}
\subsection{Two-dimensional model problem for an elastic solid}
\subsubsection{Introduction}
\subsubsection{Equations of motion and constitutive equations}
\textbf{Equation of motion}\\
\textbf{Constitutive equation}
\subsubsection{Model problem}
\textbf{Problem 2D-1}
\subsubsection{Variational form}
\textbf{Bilinear forms and integral}\\
\textbf{Test functions for problem 2D-1}\\
\textbf{Problem 2D-1V}
\subsection{Timoshenko beam models}
\subsubsection{Equations of motion and constitutive equations}
\subsubsection{Boundary conditions}
\subsubsection{Boundary value problems}
\subsubsection{Variational form}
\textbf{Function spaces}\\
\textbf{Test function spaces for different problems}\\
\textbf{Bilinear forms}
\subsection{Reissner-Mindlin Plate Model}
\subsubsection{Equations of Motion and Constitutive Equations}
\subsubsection{Dimensionless Form}
\textbf{Remark}\\
\textbf{Dimensionless Equations of Motion}\\
\textbf{Dimensionless Constitutive Equations}
\subsubsection{Boundary Conditions}
\subsubsection{Model Problems}
\textbf{Problem P-1}\\
\textbf{Problem P-2}
\subsubsection{Variational Form}
\textbf{Bilinear Forms and integral}\\
\textbf{Test Functions for Problem P-1}\\
\textbf{Problem P-1V}
\subsection{Rod Theory}
\section{Mathematical analysis of vibration problems}
\subsection{Introduction}
\textbf{Problem T-2W}
\subsection{Existence and uniqueness of solutions}
\subsubsection{The variational approach}
\subsubsection{Main results for existence and uniqueness}
\subsubsection{First order system}
\subsection{Application: Timoshenko beam model}
\subsection{Modal analysis}
\subsubsection{Timoshenko beam}
\subsubsection{General vibration problem}
\section{Finite element theory}
\subsection{Introduction}
\subsection{Convergence of the Galerkin approximation}
\subsubsection{Galerkin approximation}
\subsubsection{System of ordinary differential equations}
\subsubsection{Error estimates}
\subsubsection{Main result}
\subsubsection{Obtaining the error estimate}
\textbf{Semi-discrete problem}
\subsubsection{Fully discrete Galerkin finite element approximation}
\textbf{Notation}\\
\textbf{Error estimate for the fully discrete problem}
\subsection{Convergence of eigenvalues in Finite Element Analysis}
\subsubsection{Eigenvalue problem for vibration problem}
\textbf{Problem GVarE}
\subsubsection{Interpolation theorem}
\subsubsection{Eigenvalue problem for our models*********}
\textbf{Notation}
\subsubsection{Convergence of the eigenvalues}
\subsubsection{Convergence of the eigenfunctions}
\subsection{Example}
\textbf{Problem 2D-1V}\\
\textbf{Test functions}
\subsubsection{Weak variational form}
\textbf{Problem 2D-1W}
\section{Timoshenko beam model}
\subsection{Introduction}
\subsection{Eigenvalue problem}
\textbf{General eigenvalue problem}\\
\textbf{Case $\bm {\lambda <\alpha }$}\\
\textbf{Case $\bm { \lambda =\alpha }$}\\
\textbf{Case $\bm {\lambda >\alpha }$}
\subsection{Cantilever beam}
\subsubsection{Calculating the eigenvalues}
\subsubsection{Example of mode shapes}
\subsection{Free-free timoshenko beam}
\subsubsection{Calculating the eigenvalues}
\subsubsection{Example of mode shapes}
\subsection{Suspended beam model}
\textbf{Variational problem}
\subsection{SP06}
\subsubsection{Mathematical models}
\textbf{Problem 3D-2}
\subsubsection{Experimental setup}
\subsubsection{Results from SP06}
\subsection{Cantilever Timoshenko beam with tip-body}
\subsubsection{The model problem}
\textbf{Boundary conditions}\\
\textbf{Remark}
\subsubsection{Variational form}
\textbf{Remark}\\
\textbf{Interface equation}\\
\textbf{Problem Var}
\subsubsection{Galerkin approximation}
\textbf{Problem G}
\subsubsection{System of ordinary differential equations}
\textbf{Problem ODE}
\subsubsection{Numerical results}
\textbf{Case: Control}\\
\textbf{Case: Decrease $\gamma $}\\
\textbf{Case: Decrease $\mu $}\\
\textbf{Case: Increase $m$}
\section{Finite element method}
\subsection{Introduction}
\subsection{Two-dimensional cantilever body}
\textbf{Reference configuration for rectangular cross-section}\\
\textbf{Cantilever elastic body}\\
\textbf{Problem 2D-1V}\\
\textbf{Constitutive equations:}\\
\textbf{Bilinear form:}
\subsubsection{Weak variational form}
\textbf{Problem 2D-1WV}
\subsubsection{Galerkin approximation}
\textbf{Problem 2D-1G}
\subsubsection{System of differential equations}
\textbf{FEM matrices}\\
\textbf{Problem 2D-1ODE}\\
\textbf{Remark}
\subsubsection{Eigenvalue problem}
\textbf{Problem 2D-1E}
\subsection{Three-dimensional elastic model}
\textbf{Reference configuration for rectangular cross-section}\\
\textbf{Cantilever elastic body}\\
\textbf{Problem 3D-1V}\\
\textbf{Bilinear Form}
\subsubsection{Weak variational form}
\textbf{Bilinear form}\\
\textbf{Problem 3D-1W}
\subsubsection{Galerkin approximation}
\textbf{Problem 3D-1G}
\subsubsection{System of ordinary differential equations}
\textbf{FEM matrices}\\
\textbf{Problem 3D-1ODE}
\subsubsection{Eigenvalue problem}
\textbf{Problem 3D-1E}
\subsection{Cantilever plate model}
\textbf{Reference configuration for a rectangular plate}\\
\textbf{Cantilever plate model}\\
\textbf{Problem P-1V}\\
\textbf{Constitutive Equations}\\
\textbf{Bilinear Form}
\subsubsection{Weak variational form}
\textbf{Bilinear forms}\\
\textbf{Problem Plate-1W}\\
\textbf{Existence and uniqueness}
\subsubsection{Galerkin approximation}
\textbf{Problem P-1G}
\subsubsection{System of ordinary differential equations}
\textbf{FEM matrices}\\
\textbf{Problem P-1ODE}
\subsubsection{Eigenvalue problem}
\textbf{Problem P-1E}
\section{Validity of cantilever beam and plate models}
\subsection{Introduction}
\textbf{Parameters}
\subsection{Validity of the Timoshenko beam model}
\subsubsection{The models}
\subsubsection{Accuracy of the numerical eigenvalues}
\subsubsection{Comparing the shape of the eigenfunctions}
\textbf{Shapes relating to beam-type eigenvalues}\\
\textbf{Shapes relating to non-beam type eigenvalues}\\
\textbf{Shapes of the cross-section}\\
\textbf{Direct comparison of mode shapes}\\
\textbf{Remark}
\subsubsection{Comparing the eigenvalues}
\textbf{Results of [LVV09]}
\subsubsection{Comparison of the eigenvalues}
\subsection{Validity of the two-dimensional elastic model}
\subsubsection{The models}
\subsubsection{Accuracy of the numerical eigenvalues}
\subsubsection{Comparing the mode shapes}
\textbf{Mode shapes relating to beam type eigenvalues.}\\
\textbf{Mode shapes relating to non-beam type eigenvalues that are present in the two-dimensional model.}\\
\textbf{Mode shapes relating to non-beam type eigenvalues that are not present in the two-dimensional model.}
\subsubsection{Comparing the eigenvalues}
\subsubsection{$b > h$}
\subsection{Validity of the Reissner-Mindlin plate model}
\subsubsection{Comparing the mode shapes}
\subsubsection{Comparing the eigenvalues}
\section{Overview}
\subsection{Overview}
\section{Conclusion}
\subsection{Overview}
\textbf{Properties}\\
\textbf{Properties of Type One}\\
\textbf{Properties of Type Two}\\
\textbf{Properties}
\subsection{Introduction}
\textbf{Different Research Approaches}\\
\textbf{Motivation}
\subsection{NRF Research Proposal}
\subsection{Modelling a Suspension Bridge: A Brief History}
\subsection{Modelling a suspension bridge: An Engineering Example}
\subsection{Simplified Mathematical Model for a Suspended Beam}
\subsubsection{Reference Configuration}
\subsubsection{System of Equations}
\textbf{Equations of Motion}\\
\textbf{Constitutive Equations}\\
\textbf{Dimensionless Equations}
\subsubsection{Boundary Conditions}
\subsection{Analysis of a Thermoelastic Timoshenko Beam Model}
\textbf{Dimensionless Equations}
\subsection{An Elastically Clamped Beam Model}
\textbf{Boundary Conditions}\\
\textbf{Hooke's law in two-dimensions}

\begin{itemize}
	\item Chapter 1: Models, Dimensionless, Variational Forms, Modal Analysis
	\item Chapter 2: Example Weak Variational, Existence and Uniqueness from [VV02], Application to example
	\item Chapter 3: Example Galerkin, Convergence of Galerkin [BV13], Application to example, Convergence of Eigenvalues using FEM
	\item Chapter 4: Eigenvalues of Timo [VV06], Example of applications on models, Emperical Study of validity [SP06], Cantilever with Tip-Body (Example why need validity)
	\item Chapter 5: FEM of 2D, 3D, and Plate
	\item Chapter 6: Validity of 1D, Validity of 2D, Validity of Plate
	\item Chapter 7: Conclusion
\end{itemize}
